%-------------------------
% Hamilton County Applications Analyst 2 Cover Letter in LaTeX
% Author : Jeffrey Perdue
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\begin{document}

\begin{flushright}
Jeffrey Perdue\\
513-462-6478\\
\href{mailto:jeffrey.perdue@gmail.com}{jeffrey.perdue@gmail.com}\\
\href{https://linkedin.com/in/jeffperdue/}{linkedin.com/in/jeffperdue/}
\end{flushright}

\vspace{10pt}

Hiring Committee\\
Hamilton County Job \& Family Services\\
222 E. Central Parkway\\
Cincinnati, OH 45202

\vspace{10pt}

Dear Hiring Committee,

I am writing to express my interest in the Applications Analyst 2 (Applications Programmer) position with Hamilton County Job \& Family Services. As a Software Engineering student graduating in May 2026, with hands-on experience in SQL, Java/Spring Boot, and enterprise data platforms, I am excited by the opportunity to apply my skills across the full System Development Life Cycle in support of mission-driven public services.

In my current role as a Software Engineering Intern at Kroger Technology, I have designed and implemented production-grade SQL applications and backend services that closely mirror the responsibilities described in your posting. I engineered reconciliation logic in SQL Server using CTEs and window functions to manage incremental purchase order loads and protect against silent data drift, and I built a Spring Boot--based monitoring scheduler to detect stale device telemetry and generate structured alerts. These projects required careful requirements analysis, application design, coding, testing, troubleshooting production-like issues, and documenting behavior so that others could operate and maintain the solutions effectively.

Beyond pure development, I have experience working with stakeholders and end users to clarify needs and translate them into specifications and documentation. As technical owner of an internal mapping application standardizing temperature zone codes across distribution centers, I collaborated with operational teams to understand their pain points, defined inputs and outputs, and ensured the resulting solution met their reporting and workflow needs. My prior experience as a Front End Supervisor at Costco, where I helped analyze operational data and trained team members on new processes, further strengthened my ability to communicate clearly, lead small groups, and support users as they adopt new tools and procedures.

I am particularly drawn to this role because it combines application development with ongoing maintenance, user support, and documentation within a public-sector context. I am comfortable working independently as well as part of a team, and I enjoy digging into complex problems, collecting data, and drawing conclusions that lead to practical, well-documented solutions. While I have significant experience with SQL, Java, web technologies, and modern enterprise platforms, I am also eager to learn and adopt the specific tools and frameworks you employ, and to grow into a resource for other Information Systems staff over time.

Thank you for considering my application. I would welcome the opportunity to discuss how my background in software engineering, data-centric application development, and user-focused support can contribute to the work of Hamilton County Job \& Family Services. I am available at your convenience and can provide any additional information you may need.

Sincerely,\\

Jeffrey Perdue

\end{document}

