%-------------------------
% Munich Re Business Analyst Cover Letter in LaTeX
% Author : Jeffrey Perdue
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\begin{document}

\begin{flushright}
Jeffrey Perdue\\
513-462-6478\\
\href{mailto:jeffrey.perdue@gmail.com}{jeffrey.perdue@gmail.com}\\
\href{https://linkedin.com/in/jeffperdue/}{linkedin.com/in/jeffperdue/}
\end{flushright}

\vspace{10pt}

Hiring Manager\\
Munich Re, US Operations\\
Enterprise Information Management (EIM)

\vspace{10pt}

Dear Hiring Manager,

I am excited to apply for the Business Analyst role supporting the GSI EIM Data Analyst teams. I am a Bachelor of Science student in Applied Software Engineering at Northern Kentucky University and a Software Engineering Intern with Kroger Technology's End-to-End Fresh organization, where I work at the intersection of data platforms, analytics, and business operations. Munich Re's push to modernize its GSI data landscape is exactly the kind of challenge I want to grow into.

At Kroger, I have contributed to analytics and data platform initiatives that support production-adjacent supply chain systems. I helped engineer a scheduler service that monitors telemetry gaps, queries SQL Server for stale device records, and triggers structured alerts so operations teams can act before data quality impacts reporting. I also designed version-aware reconciliation logic using SQL CTEs and window functions to compare incoming purchase order loads with warehouse tables, preventing silent drift and preserving historical correctness. These projects deepened my experience with SQL, data warehousing concepts, and data quality, and taught me how to turn fuzzy operational problems into concrete analytical work.

I am comfortable working as an analyst across the requirements lifecycle. I clarify ambiguous requests into user stories and acceptance criteria, collaborate with product owners and other analysts in Agile ceremonies, and document changes so they remain understandable months later. I am used to project tracking tools such as Jira and to supporting production issues by investigating data discrepancies, updating documentation, and clearly communicating status to stakeholders who rely on accurate reports.

My projects and research echo the core of this role. I built a requirements risk analysis platform that surfaces structural and compliance issues in requirements artifacts and produces reports that help stakeholders prioritize follow-up work. In another project, I designed a safety-critical menu system that treats allergen information as structured data with clear ownership, which reinforced the importance of data governance, integrity, and traceability in real products.

I am drawn to Enterprise Information Management because of its mandate to build scalable, governed data solutions that directly support business decisions. I would be thrilled to bring my background in SQL, data warehousing, requirements analysis, and Agile delivery to your GSI data teams, and to keep learning from Munich Re's risk and data experts. Thank you for your time and consideration; I would welcome the chance to discuss how I can contribute to your data modernization efforts.

Sincerely,\\

Jeffrey Perdue

\end{document}

