%-------------------------
% Tailored Resume for Cleveland-Cliffs
% Author : Jeffrey Perdue (adapted)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Jeffrey Perdue} \\ \vspace{1pt}
    \small 513-462-6478 $|$ \href{mailto:jeffrey.perdue@gmail.com}{\underline{jeffrey.perdue@gmail.com}} $|$
    \href{https://linkedin.com/in/jeffperdue/}{\underline{linkedin.com/in/jeffperdue/}} $|$
    \href{https://github.com/jeffreyperdue}{\underline{github.com/jeffreyperdue}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\resumeItemListStart
\resumeItem{Motivated software engineer with hands-on experience building enterprise applications, data pipelines, and embedded systems. Comfortable working with cross-functional teams to translate operational needs into reliable software solutions. Eager to contribute to manufacturing-focused IT at Cleveland-Cliffs and rapidly learn platform-specific technologies such as Angular or .NET/C#.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Northern Kentucky University}{Highland Heights, KY}
{Bachelor of Science in Applied Software Engineering, Minor in Computer Science, GPA: 3.9}{May 2026}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Relevant Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}: Java, Python, TypeScript, SQL, Embedded C/C++ \\
\textbf{Frameworks \& Frontend}: React (strong), familiarity with TypeScript-based frameworks; quick to learn Angular \\
\textbf{Backend \& Platforms}: Spring Boot, REST APIs, experience integrating services and databases; learning .NET / C# for enterprise apps \\
\textbf{Data \& Databases}: SQL Server, Azure Synapse, Databricks; designed reconciliation and ETL logic \\
\textbf{Practices}: Agile/Kanban, Git, code reviews, CI concepts, system integrtation, technical documentation
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineering Intern}{August 2025 -- April 2026}
{Kroger Technology -- End-to-End Fresh}{Blue Ash, OH}
\resumeItemListStart
\resumeItem{Developed backend services and enterprise data integrations supporting production-adjacent operations using Spring Boot, SQL Server, Azure Synapse, and Databricks.}
\resumeItem{Engineered a Spring Boot scheduler to monitor device telemetry gaps, query SQL Server for stale records, and dispatch OAuth2-authenticated alert summaries with robust error handling and testable design.}
\resumeItem{Designed production-grade SQL reconciliation logic (CTEs, window functions, anti-joins) to manage incremental loads and ensure data consistency across systems.}
\resumeItem{Served as technical owner for a centralized mapping application to standardize temperature zone codes across distribution centers, coordinating stakeholder requirements and controlled business updates.}
\resumeItem{Participated in Agile workflows, sprint planning, code reviews, and cross-functional collaboration with operations and engineering teams to deliver reliable features.}
\resumeItemListEnd

\resumeSubheading
{Front End Supervisor}{June 2020 -- August 2025}
{Costco Wholesale}{Columbus, OH; Florence, KY}
\resumeItemListStart
\resumeItem{Led operational teams and used data-driven analysis to diagnose workflow bottlenecks and implement process improvements for a high-volume department serving major revenue streams.}
\resumeItem{Collaborated with management to translate operational requirements into staffing, training, and tooling changes — experience directly applicable to manufacturing/operations partnerships.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{StillCold — BLE-Based Embedded Temperature Monitoring}}{ESP32-C6, Arduino Nano, BLE, I\textsuperscript{2}C}
\resumeItemListStart
\resumeItem{Architected a modular embedded system separating sensing from wireless exposure; implemented periodic sensor acquisition and BLE characteristics to reliably surface temperature telemetry.}
\resumeItem{Validated end-to-end data flow and designed for low-overhead deterministic operation — relevant to device telemetry and manufacturing sensor integrations.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{StressSpec — Requirements Risk Analysis Platform}}{Python, FastAPI}
\resumeItemListStart
\resumeItem{Built a rule-based analysis platform to detect requirement risks and export prioritized findings to support decision-making and process improvement.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ADDITIONAL-----------
\section{Additional Info}
\resumeSubHeadingListStart
\resumeItemListStart
\resumeItem{Willing to work on-site full-time (5 days/week).}
\resumeItem{Familiar with enterprise development practices, eager to upskill to COBOL/mainframe or .NET as needed for integrations and legacy systems.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
